Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-20 RR_manuscript/Draft_RR.Rmd
add categorical factors table and printing function

# number of analyses
msa_models_unique <- msa_models %>%
  select(animal, model_n, outcome, typicality_operationalization, framework, model, temporal_window, random_effects, n_random, phon_rating, stat_rating, n_predictors, pop_pred, operationalisation, operationalisation_notes) %>%
  distinct()

@@

<!-- TODO: some of this or most of this should go into a nice overview table -->

@@

@@

tbl_team_model_desc %>% 
  select(Descriptives = desc, Metric, Range, `Mean (SD)`) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "l", "c", "r"), 
    caption = "Descriptive statistics for teams and models included in the 
    meta-analysis (n = 30).",
    label = "team-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 11)

@@

>>>>

# number of analyses
# JVC: Why is this the number of total analyses and not nrow(msa_models)?
msa_models_unique <- msa_models %>%
  select(animal, model_n, outcome, typicality_operationalization, framework, model, temporal_window, random_effects, n_random, phon_rating, stat_rating, n_predictors, pop_pred, operationalisation, operationalisation_notes) %>%
  distinct()

@@

@@

# Print values from tibble for article
pull_from_tib <- function(df, col, row, val) {
  col <- enquo(col)
  row <- enquo(row)
  val <- enquo(val)
  val <- filter(df, !!col == !!row) %>% pull(!!val)
  return(val)
}

@@

tbl_team_model_desc %>% 
  select(Descriptives = desc, Metric, Range, `Mean (SD)`) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "l", "c", "r"), 
    caption = "Descriptive statistics for teams and models included in the 
    meta-analysis (n = 30).",
    label = "team-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 10)

@@

<!-- Begin Table 2 --> 
\vspace{0.2in}
```{r}
#| label: categorical-descriptives-table
#| echo: false
#| results: 'asis'
#| eval: true

# Descriptives of categorical variables
tbl_categorical_desc <- msa_models %>% 
  select(animal, outcome, temporal_window, typicality_operationalization, 
  framework, model) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "val") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  count(val) %>% 
  group_by(metric) %>% 
  mutate(prop = n / sum(n), perc = prop * 100, 
    Metric = case_when(
      metric == "temporal_window" ~ "Temporal window", 
      metric == "typicality_operationalization" ~ "Typicality operationalization", 
      TRUE ~ metric
    ), 
    Metric = str_to_sentence(Metric), 
    Type = case_when(
      val != "GAM" ~ str_to_sentence(val), 
      TRUE ~ val
    )) %>% 
  mutate(across(c("prop", "perc"), specify_decimal, k = 2)) %>% 
  unite(label, c("metric", "val")) %>% 
  mutate(label = str_replace_all(label, " ", "_"), 
         label = str_remove_all(label, "\\(|\\)"))

tbl_categorical_desc %>% 
  select(Metric, Type, n, `\\%` = perc) %>% 
  mutate(Metric = case_when(
    Type != "Bayesian" & Metric == "Framework" ~ " ", 
    Type != "GAM" & Metric == "Model" ~ " ", 
    Type != "Duration" & Metric == "Outcome" ~ " ", 
    Type != "Other" & Metric == "Temporal window" ~ " ", 
    Type != "Categorical" & Metric == "Typicality operationalization" ~ " ", 
    TRUE ~ Metric)
    ) %>% 
  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 2) %>%
  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 6) %>%
  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 12) %>%
  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 18) %>%
  mutate(across(-c("Metric", "Type"), ~replace(., is.na(.), " "))) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "l", "r", "r"), 
    caption = "Descriptive statistics for model stuff.",
    label = "categorical-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 10)

# pull_from_tib(tbl_categorical_desc, label, "framework_bayesian", n)

```
<!-- END Table 2 -->

### 2022-09-20 RR_manuscript/Draft_RR.tex
add categorical factors table and printing function

\caption{\label{tab:team-descriptives-table}Descriptive statistics for teams and models included in the 
    meta-analysis (n = 30).}
\centering
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{llcr}
\toprule
Descriptives & Metric & Range & Mean (SD)\\
\midrule
Teams & Overall peer review rating & 39--89 & 69.95 (14.34)\\
 & Acoustic analysis rating & 41--88 & 71.51 (13.92)\\
 & Prior belief in $H_{1}$ & 48--92 & 69.19 (11.33)\\
 & Self-report statistical ability & 33--93 & 69.46 (16.52)\\
 & Years since PhD & -4--12 & 4.77 (4.16)\\
 &  &  & \\
Models & n. coefficients & 1--11 & 3.50 (2.75)\\
 & n. models & 1--16 & 3.67 (3.44)\\
 & n. predictors & 1--4 & 1.59 (0.85)\\
 & n. random effects & 0--10 & 2.47 (2.05)\\
 & n. random intercepts & 0--10 & 1.91 (1.77)\\
 & n. random slopes & 0--4 & 0.63 (1.07)\\
 & n. random smooths & 0--0 & 0.00 (0.00)\\
 & n. terms & 1--4 & 1.78 (1.08)\\
\bottomrule
\end{tabular}
\end{table}
\vspace{0.2in}

>>>>

\caption{\label{tab:team-descriptives-table}Descriptive statistics for teams and models included in the 
    meta-analysis (n = 30).}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{llcr}
\toprule
Descriptives & Metric & Range & Mean (SD)\\
\midrule
Teams & Overall peer review rating & 39--89 & 69.95 (14.34)\\
 & Acoustic analysis rating & 41--88 & 71.51 (13.92)\\
 & Prior belief in $H_{1}$ & 48--92 & 69.19 (11.33)\\
 & Self-report statistical ability & 33--93 & 69.46 (16.52)\\
 & Years since PhD & -4--12 & 4.77 (4.16)\\
 &  &  & \\
Models & n. coefficients & 1--11 & 3.50 (2.75)\\
 & n. models & 1--16 & 3.67 (3.44)\\
 & n. predictors & 1--4 & 1.59 (0.85)\\
 & n. random effects & 0--10 & 2.47 (2.05)\\
 & n. random intercepts & 0--10 & 1.91 (1.77)\\
 & n. random slopes & 0--4 & 0.63 (1.07)\\
 & n. random smooths & 0--0 & 0.00 (0.00)\\
 & n. terms & 1--4 & 1.78 (1.08)\\
\bottomrule
\end{tabular}
\end{table}
\vspace{0.2in}

\caption{\label{tab:categorical-descriptives-table}Descriptive statistics for model stuff.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{llrr}
\toprule
Metric & Type & n & \%\\
\midrule
Framework & Bayesian & 34 & 20.00\\
 & Frequentist & 136 & 80.00\\
 &  &  & \\
Model & GAM & 2 & 1.18\\
 & Linear model & 166 & 97.65\\
 & Other & 2 & 1.18\\
 &  &  & \\
Outcome & Duration & 57 & 33.53\\
 & F0 & 62 & 36.47\\
 & Formants & 24 & 14.12\\
 & Intensity & 22 & 12.94\\
 & Other & 5 & 2.94\\
 &  &  & \\
Temporal window & Other & 8 & 4.73\\
 & Phrase & 6 & 3.55\\
 & Segment & 76 & 44.97\\
 & Sentence & 4 & 2.37\\
 & Word & 75 & 44.38\\
 &  &  & \\
Typicality operationalization & Categorical & 135 & 80.36\\
 & Continuous (mean) & 30 & 17.86\\
 & Continuous (median) & 3 & 1.79\\
\bottomrule
\end{tabular}
\end{table}
